Output Summary

### 2023-04-04 03-post-process/output-plots.Rmd
Create object storing the indices of lwr triangle rhos
E.g., [2,1], [3,1], etc. Useful later.

This change should have been included with an earlier commit on rho plotting

# make the labels for which elements of the rho matrices contain unique elements
dummy_cols = matrix(rep(1:jags_data$nj, each = jags_data$nj), jags_data$nj, jags_data$nj)
dummy_rows = matrix(rep(1:jags_data$nj, jags_data$nj), jags_data$nj, jags_data$nj)
vcov_cols = dummy_cols[lower.tri(dummy_cols)]
vcov_rows = dummy_rows[lower.tri(dummy_rows)]
vcov_labels = paste0(pops[vcov_rows], "-", pops[vcov_cols])
```

>>>>

# make the labels for which elements of the rho matrices contain unique elements
dummy_cols = matrix(rep(1:jags_data$nj, each = jags_data$nj), jags_data$nj, jags_data$nj)
dummy_rows = matrix(rep(1:jags_data$nj, jags_data$nj), jags_data$nj, jags_data$nj)
vcov_cols = dummy_cols[lower.tri(dummy_cols)]
vcov_rows = dummy_rows[lower.tri(dummy_rows)]
vcov_inds = paste0("[", vcov_rows, ",", vcov_cols, "]")
vcov_labels = paste0(pops[vcov_rows], "-", pops[vcov_cols])
```
